BIP32-Ed25519++: A More Secure Hierarchical Deterministic Wallet Standard for Ed25519 Keys

### 2024-06-13 paper.tex
clarify "level"/hardening for indices

Each level has $2^{32}$ possible values.
When hardening a level, the most-significant bit is set to 1.
Thus $[0, 2^{31})$ are reserved for non-hardened keys, and $[2^{31}, 2^{32})$ are reserved for hardened keys.

>>>>

There are $2^{32}$ possible values for the address index (\verb=key=).
In a hardened index, the most-significant bit is set to 1.
So, the interval $[0, 2^{31})$ is for non-hardened keys, and $[2^{31}, 2^{32})$ is for for hardened keys.
